Untitled

### 2025-03-20 script/r/draft.Rmd
MAJ path
maj wb_gov

@@

>>>>

```{r}
setwd("~/working_paper/rbci/")
getwd()
```

@@

```{r}
library(readxl)
library(tidyr)

countries <- data_final %>% filter(spl == 1) %>% pull(iso) %>% unique()

wb_gov <- read_excel("data/data_raw/wb_gov/wgidataset.xlsx")

wb_gov %<>%
  select(code, year, indicator, estimate) %>%
  mutate(estimate = na_if(estimate, ".."))

wb_gov %<>%
  pivot_wider(names_from = indicator, values_from = estimate)

wb_gov %<>%
  rename(
    ctrl_corr = cc,
    voice_acc = va,
    pol_stab = pv,
    gov_eff = ge,
    reg_qty = rq,
    rol = rl,
    iso = code
  ) %>%
  mutate(across(c(
    ctrl_corr, voice_acc, pol_stab, gov_eff, reg_qty
  ), as.numeric))

wb_gov %<>%
  mutate(round = case_when(
    between(year, 2011, 2013) ~ 5,
    between(year, 2014, 2015) ~ 6,
    between(year, 2016, 2018) ~ 7,
    between(year, 2019, 2021) ~ 8,
    TRUE ~ NA_integer_
  ))

wb_gov %<>%
  group_by(iso, round) %>%
  filter(!is.na(round)) %>%
  mutate(
    ctrl_corr_mean = ifelse(all(is.na(ctrl_corr)), NA_integer_, mean(ctrl_corr, na.rm = TRUE)),
    voice_acc_mean = ifelse(all(is.na(voice_acc)), NA_integer_, mean(voice_acc, na.rm = TRUE)),
    pol_stab_mean = ifelse(all(is.na(pol_stab)), NA_integer_, mean(pol_stab, na.rm = TRUE)),
    gov_eff_mean = ifelse(all(is.na(gov_eff)), NA_integer_, mean(gov_eff, na.rm = TRUE)),
    reg_qty_mean = ifelse(all(is.na(reg_qty)), NA_integer_, mean(reg_qty, na.rm = TRUE))
  ) %>%
  ungroup()

wb_gov %<>%
  select(
    iso,
    round,
    ctrl_corr_mean,
    voice_acc_mean,
    pol_stab_mean,
    gov_eff_mean,
    reg_qty_mean
  ) %>%
  distinct(iso, round, .keep_all = TRUE)

wb_gov %<>%
  filter(iso %in% countries)
```
